Untitled

### 2017-07-30 Average local prices.Rmd
Local prices tweak

@@

@@

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent, LAD11CD) %>%
  mutate(outcome = LUPdepExt>Extent)  %>% 
  left_join(LocalMean, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
  mutate(priceRatio = (price/LocalMean)) #%>%
  #select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)

test %>%
  ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour = priceRatio>1)) + geom_jitter()

rpart.model <- rpart(as.factor(absdiff>0) ~ maxPerc, test)
rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
rpart.model2 <- rpart(as.factor(absdiff>0) ~ priceRatio+ maxPerc, test)
rpart.model3 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc + priceRatio, test)

@@

>>>>

#this uses rank I think it should be dist check this

@@

LocalMean <- NetworkDist %>% 
  gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=3) %>%
#join on the average prices per LAD
  left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
  filter(LAD11CD=="E07000029")

@@

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent, LAD11CD) %>%
  mutate(outcome = LUPdepExt>Extent)  %>% 
  left_join(LocalMean, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
  mutate(priceRatio = (price/LocalMean)) %>%
  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price>LocalMean ) #%>%
#select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)
#remove barrow
#filter(LAD11CD !="E07000027")

test %>%
  filter(maxPerc<10) %>%
  ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour = priceRatio>1)) + geom_jitter()

test %>%
  filter(maxPerc<10) %>%
  ggplot(.,aes(x= Extent, y = LUPdepExt, colour = absdiff>0)) + geom_jitter()

test2 <- test %>% 
  select(LAD11NM, absdiff, LUPdepExt, Extent, LocalMean, price, priceRatio, maxPerc) %>%
  mutate(LUPdepExt.Extent = LUPdepExt>Extent, price.LocalMean = price>LocalMean ) %>%
  filter( price.LocalMean == FALSE)

table(test$maxPerc>5, test$LUPdepExt.Extent>0, test$absdiff>0)

rpart.model <- rpart(as.factor(absdiff>0) ~ maxPerc, test)
rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt.Extent + maxPerc + priceRatio, test)
rpart.model3 <- svm(as.factor(absdiff>0) ~ LUPdepExt+Extent + maxPerc + priceRatio, test, type = "C", kernel = "radial")
rpart.model3 <- svm(as.factor(absdiff>0) ~ maxPerc + LUPdepExt+ Extent, test, type = "C", kernel = "radial")

@@

test2 <- test[predict(rpart.model2, test, type = "class")!=as.factor(test$absdiff>0),]

### 2017-07-30 PaperCode.Rmd
Local prices tweak

@@

```{r}
#Wiltshire have not included everything
# WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts.xlsx",
#                                sheet=1)[1:4] %>%
#   StructureData()
```

@@

@@

@@

@@

setwd(file.path(RegionsComp, "Region North East"))
#Not sure all are there ask for confirmation
# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(2:4,6,8:10))

@@

@@

#load full data
BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")

#Include only full price standard purchases
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")

#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

@@

elementnames<- names(BootStrapRES)

@@

@@

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_point()

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_point()

@@

test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_point()

svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
#why do the two rforest models have such different results
rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)

@@

library(e1071)
 library(rpart)
 data(Glass, package="mlbench")
 ## split data into a train and test set
 index <- 1:nrow(Glass)
 testindex <- sample(index, trunc(length(index)/3))
 testset <- Glass[testindex,]
 trainset <- Glass[-testindex,]

svm.model <- svm(Type ~ ., data = trainset, cost = 100, gamma = 1)
svm.pred <- predict(svm.model, testset[,-10])

rpart.model <- rpart(Type ~ ., data = trainset)
rpart.pred <- predict(rpart.model, testset[,-10], type = "class")

confusionMatrix( rpart.pred, testset$Type)
confusionMatrix( svm.pred, testset$Type)
```

>>>>

#this uses rank for distance from LAD I think it should be dist check this

@@

```{r}
#Wiltshire have not included everything
WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = 3:8)
```

@@

BrecklandsDATA <- read_excel("BFOI-003031 BrecklandDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData()

#they deleted the classes
SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
  StructureData()

@@

HuntingdonDATA <- read_excel("Huntingdonshire  FOI 568discounts.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = 2:8)

PeterboroughDATA <- read_excel("Peterborough 1707267585 completed.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(4,6:7,11))

@@

# HambletonDATA <- read_excel("HDC1088.xlsx")[,1:4] %>%
#  StructureData()

ScarboroughDATA <- read_excel("FOIA 5156 Scarborough Discounts LSOA.xlsx"  )[,1:4]%>%
  StructureData(2:8)

@@

setwd(file.path(RegionsComp, "Region North East"))
list.files()
#Not sure all are there ask for confirmation
# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(2:4,6,8:10))

NewcastleDATA <- read_excel("Newcastle upon TyneDiscountsLSOA.xlsx", sheet=1)%>% .[,c(1,3:5)] %>%
    StructureData(lowuse = 2:7)

#FOr some reason Gateshead has the wrong LAD11CD I don't know why. I have changed it to the right one but feel that perhaps I should check them all, but how?
GatesheadDATA <- read_excel("Copy of GatesheadExemptionsLSOA.XLSX"   , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:3, 20,22:25)) %>%
  mutate(LAD11CD = ifelse(is.na(LAD11CD), NA, "E08000037"))

##Durham
```{r}
  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
    StructureData()

  HartlepoolData <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
    StructureData(2:7)

@@

#Conway have sen the wrong stuff  
# ConwayDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
#   rename(Postcode = geo_postcode) %>%
#   mutate(Postcode = sub(" ", "", Postcode)) %>%
#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
#   StructureData()

@@

# #load full data
# BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
# 
# #Include only full price standard purchases
# BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
# 
# #Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
# BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

@@

elementnames<- names(BootStrapRESExO)

@@

```{r}
test <- BootStrapRESExO$ChelseaLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean))

test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)
```

@@

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_jitter()

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_jitter()

@@

test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
  geom_jitter()

svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
#why do the two rforest models have such different results
#rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)

@@
